Section_8_Team1_Lab2_Report

### 2021-08-05 notebooks/Draft_Report.Rmd
added r code for % coeff calc for Lucy

$$RECHECK THIS SECTION FOR VALUES$$
We will also interpret the coefficient values and what these mean in the context of our model. Almost all of our variables needed a log transform, including the output, making this a log-log regression. These regressions are most intuitive to understand in terms of percent increases.
* First to note is our persistently significant constant in each model. Regardless of any variables, we are getting between ~300 (as with model3) and over 8000 (as with model2) trips over 100 miles. This is calculated as e^(Constant).
* In $Model_1$, for every percent increase in cases, we are getting almost half a percent increase in trips. The positive relationship doesnt make much sense, so we will look to the other models.
* In $Model_2$, we see that density has a more positive relationship with trips, with every percent increase in county density modeled to a half percent increase in trips. Also the positive relationship between COVID-19 cases and trips has decreased to resulting in 0.15 and 0.25% increase in trips respectively.
* In $Model_3$, COVID-19 cases become insignificant. The coefficients have become slightly negative as in increase in cases decreases trips, which is in line with our original hypothesis, but is not significant. Instead, for every percent median income of the county increases by, the amount of long trips decrease by 0.3%. This could indicate that more affluent counties trust science and err on the safe side in the midst of COVID-19. Finally, in our 3rd model, counties with more people under 17 years of age are more likely to take long trips. Due to the time frame of our analysis, this also makes sense because june is the start of summer break when many families like to take vacations together.

>>>>

$$RECHECK THIS SECTION FOR VALUES$$
```{r calc. coeff percents}
#Model 1
#when you compare a coeff for non-log x to a log y:
(1-exp(coef(model1)["is_rural"]))*100
#For every percent increase in x 'is rural', you get a #% outcome in number of long trips.

#Model 2
(1-exp(coef(model2)["is_rural"]))*100
#Model 3
(1-exp(coef(model3)["is_rural"]))*100

#Same for income

#Model 2
(1-exp(coef(model2)["log(median_income + 1)"]))*100
#Model 3
(1-exp(coef(model3)["log(median_income + 1)"]))*100

#Same for density

#Model 2
(1-exp(coef(model2)["log(density)"]))*100
#Model 3
(1-exp(coef(model3)["log(density)"]))*100

#Same for age 17 & 65
#Model 3
(1-exp(coef(model3)["log(lt17)"]))*100
(1-exp(coef(model3)["log(gt65)"]))*100
```

We will also interpret the coefficient values and what these mean in the context of our model. Almost all of our variables needed a log transform, including the output, making this a log-log regression. These regressions are most intuitive to understand in terms of percent increases.
* First to note is our persistently significant constant in each model. Regardless of any variables, we are getting between ~300 (as with model3) and over 8000 (as with model2) trips over 100 miles. This is calculated as e^(Constant).
* In $Model_1$, for every percent increase in cases, we are getting almost half a percent increase in trips. The positive relationship doesnt make much sense, so we will look to the other models.
* In $Model_2$, we see that density has a more positive relationship with trips, with every percent increase in county density modeled to a half percent increase in trips. Also the positive relationship between COVID-19 cases and trips has decreased to resulting in 0.15 and 0.25% increase in trips respectively.
* In $Model_3$, COVID-19 cases become insignificant. The coefficients have become slightly negative as in increase in cases decreases trips, which is in line with our original hypothesis, but is not significant. Instead, for every percent median income of the county increases by, the amount of long trips decrease by 0.3%. This could indicate that more affluent counties trust science and err on the safe side in the midst of COVID-19. Finally, in our 3rd model, counties with more people under 17 years of age are more likely to take long trips. Due to the time frame of our analysis, this also makes sense because june is the start of summer break when many families like to take vacations together.
